Hybrid platforms and bargaining

### 2023-04-19 src/presentation/topics_talk.qmd
Add related literature slide

>>>>

## Related literature

::: {.incremental}
 - **Hybrid platform markets**<br>
 @anderson2021hybrid, @gutierrez2021welfare, @hagiu2022should
 - Similarly structured markets
   - Private labels in retail [@steiner2004nature]
   - Vertical integration [@hart1990vertical; @de2005vertical; @montez2007downstream]
 - Cooperative games in IO<br>
 @hart1990property, @levy1997individual, @inderst2003bargaining, @montez2007downstream
